\recipe{Chocolate Chip Oatmeal Cookies}
\servingstimes{?? cookies}{15 min}{10 min}
\category{Desserts}

\ingredients
\begin{multicols}{2}
\raggedcolumns % Don't make the second column take the vertical space of the first column
\begin{itemize}
    \item 1 cup butter
    \item 1 cup brown sugar
    \item 1 cup sugar
    \item 2 eggs
    \item 1 tsp vanilla
    \item 2 cups flour
    \item 2 \nicefrac{1}{2} cups oatmeal
    \item \nicefrac{1}{2} teaspoon salt
    \item 1 tsp baking powder
    \item 1 tsp baking soda
    \item 1 tsp cinnamon
    \item 12 oz chocolate chips
    \item 8 oz Hershey bar grated
    \item \textit{optional - }1 \nicefrac{1}{2} cup nuts

\end{itemize}
\end{multicols}

\instructions
\begin{enumerate}
    \item Measure and blend oatmeal in a blender to a fine powder. 
    \item Cream butter and both sugars.
    \item Add eggs and vanilla.
    \item Mix together with flour, oatmeal, salt, baking powder, baking soda, and cinnamon. 
    \item Add chocolate chips, candy bar, and nuts.
    \item Roll into balls and place two inches apart on a cookie sheet.
    \item Bake for 6 minutes at \temp{375}.
\end{enumerate}

\vfill

\begin{tabular}{ c | l | l }
  \textbf{Version} & \textbf{Date} & \textbf{Changes} \\ 
  \hline		
  1.0 & 2020-04-13 & Original from Ma \\
\end{tabular}



\recipe{Double Peanut Butter Cookies}
\servingstimes{18 cookies}{15 min}{20 min}
\category{Desserts}

\ingredients
\begin{multicols}{2}
\raggedcolumns % Don't make the second column take the vertical space of the first column
\begin{itemize}
    \item \nicefrac{1}{2} teaspoon vanilla extract
    \item \nicefrac{1}{2} cup butter or margarine (1 stick), softened
    \item \nicefrac{1}{3} creamy peanut butter
    \item \nicefrac{3}{4} cup sugar
    \item 1 \nicefrac{1}{4} cups all-purpose flour
    \item \nicefrac{1}{2} teaspoon baking soda
    \item \nicefrac{1}{4} teaspoon salt
    \item 1 egg
\end{itemize}
\end{multicols}

\instructions
\begin{enumerate}
    \item Heat oven to \temp{350}.
    \item Beat butter, sugar, and peanut butter in large bowl until creamy. Add egg and vanilla; beat well. Stir together flour, baking soda, and salt; gradually add to butter mixture, beating until well blended. Stir in peanut butter chips; drop by scant \nicefrac{1}{4} cupfuls onto ungreased cookie sheet - 6 cookies per sheet.
    \item Bake 12 to 16 minutes or until lightly browned around the edges. Cool 1 minute; remove from cookie sheet to wire rack. Cool completely. Makes about 18 cookies.
\end{enumerate}

\vfill

\begin{tabular}{ c | l | l }
  \textbf{Version} & \textbf{Date} & \textbf{Changes} \\ 
  \hline		
  1.0 & 2020-04-01 & Original \\
\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\recipe{Pistachio Bread}
\servingstimes{24 (2 9x5 loaves)}{15 min}{45 min}
\category{Desserts}

\ingredients
\begin{multicols}{2}
\raggedcolumns % Don't make the second column take the vertical space of the first column
\begin{itemize}
    \item 1 (18.25oz) package yellow cake mix
    \item 4 eggs
    \item \nicefrac{1}{4} cup vegetable oil
    \item 2 tablespoons water
    \item 1 (3oz) package instant pistachio pudding mix
    \item 1 cup sour cream
    \item \nicefrac{1}{2} cup maraschino cherries
    \item \nicefrac{1}{2} teaspoon green food coloring
    \item \nicefrac{1}{2} teaspoon ground cinnamon
    \item 2 tablespoons white sugar
\end{itemize}
\end{multicols}
 
\instructions
\begin{enumerate}
    \item Preheat oven to \temp{350}. Grease and flour two 9x5 inch loaf pans.
    \item Mix together cake mix, eggs, oil, water, pudding mix, sour cream, cherries, and food coloring. Pour into prepared pans. 
    \item In a small bowl, stir together cinnamon and sugar. Sprinkle tops of loaves with mixture. 
    \item Bake for 45 minutes and cool. 
\end{enumerate}

\vfill

\begin{tabular}{ c | l | l }
  \textbf{Version} & \textbf{Date} & \textbf{Changes} \\ 
  \hline		
  1.0 & 2020-08-28 & Original \\
\end{tabular}
